Local Spectral Clustering of Density Upper Level Sets

### 2019-06-24 neurips/local_spectral_density_clustering_arxiv.tex
more updates -- updates to proof of Thm 2

%%% Vectors
\newcommand{\pbf}{p}        % removed bold font
\newcommand{\qbf}{\mathbf{q}}
\newcommand{\ebf}[1]{{e}_{#1}}
\newcommand{\pibf}{\bm{\pi}}

@@

\begin{theorem}
  \label{thm: consistent_recovery_of_density_clusters}
  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
  such that if  
  \begin{equation}
    \label{eqn: kappa_ub}
    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
  \end{equation}
  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
\end{theorem}
\noindent Some remarks are in order: 
 \begin{enumerate}  
 \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
  density cluster $\Cset$ in the sense of \eqref{eqn:
    consistent_density_cluster_recovery} only when we can guarantee a very small
  fraction of points will be misclassified. This strong condition is the price
  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
 \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
  $\kappa(\Cset)$ unfortunately prevents us from making claims about the
  behavior of PPR in this regime. Although the restriction to a kernel
  function fixed in $n$ is standard for spectral clustering theory
  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
  this is merely looseness in our upper bounds.  
\end{enumerate}
\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
changed this $\epsilon$ to $\varepsilon$.}

@@

\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
~

In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.

Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$. As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
\begin{align}
\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
\end{align}
We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
\begin{align}
\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
\end{align}

>>>>

%%% Vectors
\newcommand{\pbf}{p}        % removed bold font
\newcommand{\qbf}{\mathbf{q}}
\newcommand{\ebf}[1]{{e}_{#1}}
\newcommand{\pibf}{\pi}

@@

\begin{theorem}
  \label{thm: consistent_recovery_of_density_clusters}
  Fix $\lambda > 0$, let $\Cset \in \Cbb_f(\lambda)$ be a
  $\kappa$-well-conditioned density cluster (with respect to some $\theta$), and
  additionally assume $f$ satisfies \ref{asmp: C'_bounded_density}. If Algorithm
  \ref{alg: ppr} is well-initialized, there exists a universal constant $c >  0$
  such that if  
  \begin{equation}
    \label{eqn: kappa_ub}
    \kappa(\Cset) \leq c \frac{\lambda_{\sigma}^2r^d
      \nu_d}{\Lambda_{\sigma}\Pbb(\Csig)}, 
  \end{equation}
  then the output set $\Cest \subseteq \Xbf$ is a consistent estimator for
  $\Cset$, in the sense of Definition \ref{def: consistent_density_cluster_estimation}. 
\end{theorem}
\noindent Some remarks are in order: 
 \begin{enumerate}  
 \item We note that the restriction on $\kappa(\Cset)$ imposed by \eqref{eqn:
    kappa_ub} results in a symmetric set difference \smash{$\Delta(\Csig[\Xbf],
    \Cest)$} on the order of $r^d$. In plain terms, we are able to recover a
  density cluster $\Cset$ in the sense of \eqref{eqn:
    consistent_density_cluster_recovery} only when we can guarantee a very small
  fraction of points will be misclassified. This strong condition is the price
  we pay in order to obtain the uniform bound in~\eqref{eqn: ppr_gap}. 
 \item While taking the radius of the neighborhood graph $r \to 0$ as $n \to
  \infty$ (thereby ensuring that the graph $G_{n,r}$ is sparse) is computationally
  attractive, the presence of a factor of \smash{$\log^2(1/r)/r$} in
  $\kappa(\Cset)$ prevents us from making claims about the
  behavior of PPR in this regime. Although the restriction to a kernel
  function fixed in $n$ is standard for spectral clustering theory
  \citep{schiebinger2015,vonluxburg2008}, it is an interesting question whether
  PPR exhibits some degeneracy over $r$-neighborhood graphs as $r \to 0$, or if
  this is merely looseness in our upper bounds.  
\end{enumerate}
\sbcomment{You are using $\epsilon$ here and in the future to mean different things. I have
changed this $\epsilon$ to $\varepsilon$.}

@@

%\paragraph{Proof of Theorem \ref{thm: consistent_recovery_of_density_clusters}.}
%~

In the proof that follows, every inequality will hold with probability tending to one as $n \to \infty$.
Observe that by Theorem \ref{thm: mixing_time_upper_bound} and the upper bounds $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$ and $r < \sigma/2d$ given in \eqref{eqn: initialization}, with probability one as $n \to \infty$, $\alpha \leq \frac{1}{9 \tau_{u}(\theta)}$. As a result, with probability one as $n \to \infty$, the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters} subsume the requirements of Lemma \ref{lem: setup}, and by that lemma, the following inequalities hold for each $u \in \Cset[\Xbf]$, $u' \in \Cset'[\Xbf]$:
\begin{align}
\pbf(u) & \geq \frac{4}{5} \overline{\pibf}_{n,r}(u) - \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} \nonumber \\
\pbf(u') & \leq \frac{2 \Phi_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} \label{eqn: setup_redux}
\end{align}
We will show that under the conditions of Theorem \ref{thm: consistent_recovery_of_density_clusters}, the following bounds hold with probability tending to one as $n \to \infty$:
\begin{align}
\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminwt} & \leq \frac{\degminwt}{125 \vol_{n,r}(\Csig{\Xbf})} \nonumber \\
\frac{2\widetilde{\Phi}_{n,r}(\Csig[\Xbf])}{\alpha \degminpr} & \leq \frac{\degminpr}{125 \vol_{n,r}(\Csig[\Xbf])} \label{eqn: gap_bounds}
\end{align}
